Word learning at the semantics pragmatics interface

### 2020-04-13 paper/supplementary_material.Rmd
tweak math

Our model describes a listener jointly reasoning about the referent of a speaker's utterance and trying to learn a lexicon (object--word mappings). This reasoning is contextualized by the prior probability of each referent. This prior probability is thought to be a function of the common ground shared between speaker and listener in that interacting around the objects changes the probability that they will be referred to later. We assume that the degree to which interactions around objects are integrated into the common ground and thus change the prior probability of those objects depends on the child's age.

To decide between referents, the listener reasons about what a rational speaker would say given an intended referent. This speaker is assumed to compute the informativity for each available utterance and then choose the most informative one. However, this expectation of speaker informativeness may vary and is captured by the parameter $\alpha$. In particular, we take $\alpha$ to be a function of the child's age.

>>>>

Our model describes a listener reasoning about the referent referred to by a speaker's utterance. This reasoning is contextualized by the prior probability of each referent $P(r \mid \rho_i)$ . This prior probability is thought to be a function of the common ground $\rho$ shared between speaker and listener in that interacting around the objects changes the probability that they will be referred to later. We assume that the degree to which interactions around objects are integrated into the common ground and thus change the prior probability of those objects depends on the child's age $i$.

To decide between referents, the listener reasons about what a rational speaker would say given an intended referent. This speaker is assumed to compute the informativity for each available utterance and then choose the most informative one. However, this expectation of speaker informativeness may vary and is captured by the parameter $\alpha$. In particular, we take $\alpha$ to be a function of the child's age $i$.
